Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-04-03 documents/cpm.tex
plot for black-and-white printer

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{compare_10187017}
\caption{
  \label{hyperparameter} 
  Comparison between default and optimized hyper-parameters. 
  In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
    \name\ prediction of optimized hyper-parameters is in green line. 
  The middle panel shows the \name\ flux of the optimized hyper-parameters, 
    while \name\ flux of the default hyper-parameters is in the bottom panel, 
    the two vertical blue lines indicate the location of the transit signal, 
    and signal to noise ratio is calculated in both situation. 
  The optimized hyper-parameter performs better than the default one, 
    but the results from both situation are close.}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{distortion_9822284_normal}
\caption{
  \label{distortion} 
  \name\ preserves transit signals. 
  Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284. 
  In the top panel, the black points shows the SAP flux of the pixel with the injected signal, 
    the green line is the fitting of the SAP flux, and the red line is the \name\ prediction. 
  In the bottom panel, red and green points represent the \name\ flux and fit flux, 
    while the signal value is indicated by the horizontal line. 
  \name\ largely preserves the signal while the fitting flux overfit the signal.}
\end{figure}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{compare_10187017_bw}
\caption{
  \label{hyperparameter} 
  Comparison between default and optimized hyper-parameters. 
  In the top panel, SAP flux is plotted in black, 
    \name\ prediction of default hyper parameters is in thin red line, 
    \name\ prediction of optimized hyper-parameters is in bold grey line. 
  The middle panel shows the \name\ flux of the optimized hyper-parameters, 
    while \name\ flux of the default hyper-parameters is in the bottom panel, 
    the two vertical blue lines indicate the location of the transit signal, 
    and signal to noise ratio is calculated in both situation. 
  The optimized hyper-parameter performs better than the default one, 
    but the results from both situation are close.}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{distortion_9822284_normal_bw}
\caption{
  \label{distortion} 
  \name\ preserves transit signals. 
  Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284. 
  In the top panel, the black points shows the SAP flux of the pixel with the injected signal, 
    the bold grey line is the fitting of the SAP flux, and the thin red line is the \name\ prediction. 
  In the bottom panel, red points and grey cross represent the \name\ flux and the fit flux, 
    while the signal value is indicated by the horizontal line. 
  \name\ largely preserves the signal while the fitting flux overfit the signal.}
\end{figure}
